\documentclass[14p]{article}
\usepackage {graphicx}
\usepackage {hyperref}
\usepackage{cite}
\begin{document}
\title{And he leaves the cave}
\maketitle

And so third day passed and Lev was so hungry.. so so hungry. And so he decided to go outside. But where is the exit, he wondered laying in his bed. Apart from weird hole in the ceiling, the one that was the source of light in his solitary cave, there seem to be no other way to exit the room.

After some time he woke up and decided to find an exit. He searched for a long time but without fruition. It looked like he spent ages crawling along walls searching for some hidden switch. Suddenly the rage surged and he started kicking and throwing the loose planks that were laying around. Since that was not enough he flipped a bed just to find a weird device there. He tried to push one thing, pull another. After several tries he managed to do something and the device come to life. It started to buzz and after few seconds a part of wall disappeared into thin air.

As the Lev approached the gap, he realised that this was not a desert of his youth he expected to find outside the cave. What he saw was a desolated land. At first sight nothing was growing there. Unless you count purple glass. It was the fields of purple glass that reached until the horizon. Lev could see some big creatures strolling through these fields and doing something, what appeared like grazing the shards of glass. 

There were various things flaying in the air. Some looked like jellyfish. Some were made from various other materials and appeared to be constructed, rather then natural (like flying jellyfishes, if one can call that natural). Some of them were made of wood and strings, that moved their wings as they flapped through sky casually. Some were shining as if their were made from metal.

"How could I forget this" thought Lev. The Void and its madness was were he found himself. The sight of this peculiar landscape made him remember things. The odd thing was that he had no idea why this place looked so familiar and why he knew so much about it. He knew a lot of other various things. But all of them were somehow disconnected. Something was missing in his knowledge that would bind these things together. He knew about other worlds, about other times, he remembered cities with great walls, other with great towers and floating stones around them. He even remembered floating cities or underwater cities. He also remember histories, and tales about people, and gods, and cities and countries, and worlds. But he did not remember about himself. Neither who he is, nor how he get here.

Then his eyes caught something interesting. There was some kind of pyramid far away. This structure was on the other side of what appeared to be mushroom forest (the fact of the existence of mushroom forest surprised him much less than his knowledge that these were not mushrooms, but actually a tentacles of subterranean being he liked to call \emph{moleogre}). There were some shining parts on this building but despite all his knowledge about the surroundings, this building was a complete mystery. 

And so naturally it was the only possible destination for Lev. He had to fill the gaps in his memory. And so he launched himself straight towards the pyramid (avoiding the mushroom forest).

\end{document}